Computing solution space properties of combinatorial optimization problems via generic tensor networks

### 2022-05-12 paper/paper.tex
update author list

\title{Computing solution space properties of combinatorial optimization problems via generic %programming 
tensor networks
%\thanks{\funding{...}}
}

@@

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/QuEraComputing/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in the Julia community.
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and the \href{https://github.com/JuliaMath/Primes.jl}{Primes}] package providing finite field algebra and prime number manipulation.
\end{description}

>>>>

\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks
%\thanks{\funding{...}}
}

@@

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/TensorBFS/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in the Julia community.
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and the \href{https://github.com/JuliaMath/Primes.jl}{Primes}] package providing finite field algebra and prime number manipulation.
\end{description}
